### 2010-08-17 docs/mg/mg.tex
reference mg_eps module
update the description of the tolerances based on the current version of mg_eps.f90

Beginning at the start of execution, there are several places where either cell-centered
multigrid or node-centered multigrid solves are performed.

@@

  The tolerance, $\epsilon$ is set in {\tt initial\_proj} and is:
   \begin{center}
   \begin{tabular}{ll}
   Cartesian:   & $\epsilon = 10^{-12}$ \\
   spherical:   & $\epsilon = 10^{-10}$ \\
   \end{tabular}
   \end{center}

@@

  The tolerance, $\epsilon_\mathrm{divu}$ depends on the iteration, $i$.
  We start with a loose tolerance and progressively get tighter.  The
  tolerances (set in {\tt divu\_iter}) are:
   \begin{center}
   \begin{tabular}{ll}
   Cartesian:   & $\epsilon = \left  \{ \begin{array}{ll} 
                   \min  (10^{-6\phantom{0}}, 10^{-8\phantom{0}} \cdot 10^{(\mathrm{nlevs - 1})} ) & 
                           \quad \mathrm{for}~ i \le \mathrm{init\_divu\_iter} - 2 \\
                   \min  (10^{-8\phantom{0}}, 10^{-10} \cdot 10^{(\mathrm{nlevs - 1})} ) & 
                           \quad \mathrm{for}~ i = \mathrm{init\_divu\_iter} - 1  \\
                   \min  (10^{-10}, 10^{-12} \cdot 10^{(\mathrm{nlevs - 1})} ) & 
                           \quad \mathrm{for}~ i = \mathrm{init\_divu\_iter}   \\
                                 \end{array}
                  \right .$ \\[10mm]
   spherical:   & $\epsilon = \left  \{ \begin{array}{ll} 
                    10^{-6\phantom{0}}  &
                           \quad \mathrm{for}~ i \le \mathrm{init\_divu\_iter} - 2 \, \\
                    10^{-8\phantom{0}}  &
                           \quad \mathrm{for}~ i = \mathrm{init\_divu\_iter} - 1 \, \\
                    10^{-10}  &
                           \quad \mathrm{for}~ i = \mathrm{init\_divu\_iter} \, )\\
                  \end{array}
                  \right .$ \\
   \end{tabular}
   \end{center}

@@

  There are 3 tolerances here: a relative tolerance of $\epsilon =
  10^{-10}$, an absolute tolerance of $\epsilon_\mathrm{abs} =
  \epsilon \cdot ||U^\mathrm{ADV}||_\infty / \Delta x$, and a bottom
  solver tolerance of $\epsilon_\mathrm{bottom} = 10^{-3}$ (these are
  all hard-coded in {\tt mac\_multigrid}).

@@

  The final velocity projection uses a tolerance of $\epsilon = \min(
  10^{-10}, 10^{-12} \cdot 10^{(\mathrm{nlevs} - 1)} )$.  This tolerance
  is set in {\tt advance} and passed into {\tt hgproject}.

>>>>

Beginning at the start of execution, there are several places where
either cell-centered multigrid or node-centered multigrid solves are
performed.  The outline below lists the solves one encounters, in order,
from the start of execution.  The values of the tolerances lists here
are defined in the {\tt mg\_eps} module.  To set problem-specific values
of these tolerances, place a local copy of {\tt mg\_eps.f90} in your
problem directory.

In the initialization, multigrid comes in during the initial projection
and the ``divu'' iterations.

@@

  The tolerances, {\tt eps\_init\_proj\_cart} and {\tt eps\_init\_proj\_sph}
  (for Cartesian and spherical respectively) are set in {\tt mg\_eps.f90}
  and have the default values of:
   \begin{center}
   \begin{tabular}{lll}
   Cartesian:   &  {\tt eps\_init\_proj\_cart} &= $10^{-12}$ \\
   spherical:   &  {\tt eps\_init\_proj\_sph}  &= $10^{-10}$
   \end{tabular}
   \end{center}

@@

  The overall tolerance, $\epsilon_\mathrm{divu}$ depends on the iteration, $i$.
  We start with a loose tolerance and progressively get tighter.  The
  tolerances (set in {\tt divu\_iter}) are, for Cartesian:
  {\small
   \begin{center}
   \begin{tabular}{lll}
   $\epsilon_\mathrm{divu} = \left  \{ \begin{array}{lll} 
                   \min\, \{& \!\!\!\mathtt{eps\_divu\_cart} \cdot \mathtt{divu\_iter\_factor}^2 \cdot \mathtt{divu\_level\_factor}^{(\mathtt{nlevs}-1)}, \\
                            & \!\!\!\mathtt{eps\_divu\_cart} \cdot \mathtt{divu\_iter\_factor}^2 \cdot \mathtt{divu\_level\_factor}^2 \, \} & 
                           \quad \mathrm{for}~ i \le \mathtt{init\_divu\_iter} - 2 \\[2mm]
                   \min\, \{& \!\!\!\mathtt{eps\_divu\_cart} \cdot \mathtt{divu\_iter\_factor} \cdot \mathtt{divu\_level\_factor}^{(\mathtt{nlevs}-1)}, \\
                            & \!\!\!\mathtt{eps\_divu\_cart} \cdot \mathtt{divu\_iter\_factor} \cdot \mathtt{divu\_level\_factor}^2 \, \} & 
                           \quad \mathrm{for}~ i = \mathtt{init\_divu\_iter} - 1  \\[2mm]
                   \min\, \{& \!\!\!\mathtt{eps\_divu\_cart} \cdot \mathtt{divu\_level\_factor}^{(\mathtt{nlevs}-1)}, \\
                            & \!\!\!\mathtt{eps\_divu\_cart} \cdot \mathtt{divu\_level\_factor}^2 \, \} & 
                           \quad \mathrm{for}~ i = \mathtt{init\_divu\_iter}   \\
                                 \end{array}
                  \right .$ \\[10mm]
   \end{tabular}
   \end{center}
   }
   and for spherical:
   {\small 
   \begin{center}
   \begin{tabular}{ll}
   $\epsilon_\mathrm{divu} = \left  \{ \begin{array}{ll} 
                     \mathtt{eps\_divu\_sph} \cdot \mathtt{divu\_iter\_factor}^2 &
                           \quad \mathrm{for}~ i \le \mathtt{init\_divu\_iter} - 2 \, \\[2mm]
                    \mathtt{eps\_divu\_sph} \cdot \mathtt{divu\_iter\_factor}  & 
                           \quad \mathrm{for}~ i = \mathtt{init\_divu\_iter} - 1 \, \\[2mm]
                    \mathtt{eps\_divu\_sph}  &
                           \quad \mathrm{for}~ i = \mathtt{init\_divu\_iter} \, )\\
                  \end{array}
                  \right .$ \\
   \end{tabular}
   \end{center}
   }
   The various parameters are set in {\tt mg\_eps.f90} and have the default values of:
   \begin{center}
   \begin{tabular}{ll}
   {\tt eps\_divu\_cart}     &= $10^{-12}$ \\
   {\tt eps\_divu\_sph}      &= $10^{-10}$ \\
   {\tt divu\_iter\_factor}  &= 100 \\
   {\tt divu\_level\_factor} &= 10 
   \end{tabular}
   \end{center}

@@

  There are 2 tolerances here: a relative tolerance of $\epsilon =
  \mathtt{eps\_mac} \cdot \mathtt{mac\_level\_factor}^{(\mathtt{nlevs}-1)}$, and a bottom
  solver tolerance of $\epsilon_\mathrm{bottom} = \mathtt{eps\_mac\_bottom}$.  These
  parameters are set in {\tt mg\_eps.f90} and have the default values:
   \begin{center}
   \begin{tabular}{ll}
   {\tt eps\_mac}           &= $10^{-10}$ \\
   {\tt mac\_level\_factor} &= 10 \\
   {\tt eps\_mac\_bottom}   &= $10^{-3}$
   \end{tabular}
   \end{center}

  %an absolute tolerance of $\epsilon_\mathrm{abs} =
  %\epsilon \cdot ||U^\mathrm{ADV}||_\infty / \Delta x$

@@

  The final velocity projection uses a tolerance of $\epsilon = \min \{
  \mathtt{eps\_hg\_max}, \mathtt{eps\_hg} \cdot \mathtt{hg\_level\_factor}^{(\mathtt{nlevs} - 1)} \}$.  This tolerance
  is set in {\tt hgproject} using the parameter values specified in {\tt mg\_eps.f90}.  The default 
  parameter values are:
   \begin{center}
   \begin{tabular}{ll}
   {\tt eps\_hg}     &= $10^{-12}$ \\
   {\tt eps\_hg\_max}      &= $10^{-10}$ \\
   {\tt hg\_level\_factor}  &= 10 \\
   \end{tabular}
   \end{center}
